Litrepl: Literate Paper Processor Promoting Transparency More Than Reproducibility

### 2025-01-02 paper/paper.tex
Update paper

Litrepl is a simple and lightweight text processing tool designed to recognize
and evaluate code sections within Markdown or \Latex documents. This
functionality is useful for both batch document section evaluation and
interactive coding within a text editor, provided a straightforward integration
is established.

@@

\begin{figure*}[hbt!]
  \centering
  \begin{minipage}{\textwidth}
  %lresult
  \begin{verbatim}
  \begin{result}
  ... some output ...
  [LR:/tmp/litrepl/python/partial_7b81e1e.txt]
  \end{result}
  \end{verbatim}
  %lnoresult
  \end{minipage}
  \caption{Example output in a verbatim format displayed above two columns.}
  \label{fig:partial-result}
\end{figure*}

@@

Template grammars similar to the illustrative example in Figure
\ref{fig:document-representation} are encoded for Markdown and \Latex formats.
Before each run, Litrepl calls Lark\textcite{Lark} to compile a customized
parser and uses it to access the sections.

@@

The restriction to text-only data types presents a more fundamental limitation.
Litrepl lifts this restriction by supporting text-only document formats. Both
\Latex and Markdown incorporate rich data without encoding it directly, instead
relying on side channels, such as the file system or network, to refer to such
objects. Consequently, Litrepl shares the advantages of good representation in
well-known version control systems, and the disadvantages, such as the need to
explicitly organize side-channel data transfer.

@@

Moreover, we support more performance-oriented integrations that handle
pre-parsing and piping only relevant document parts. For these approaches,
Litrepl offers the \verb|print-regexp| command, which outputs the anchor regexp
in several common formats.
% lnoresult

>>>>

Litrepl is a lightweight text processing tool designed to recognize and evaluate
code sections within Markdown or \Latex documents. This functionality is useful
for both batch document section evaluation and interactive coding within a text
editor, provided a straightforward integration is established.

@@

\begin{figure*}[hbt!]
  \centering
  \begin{minipage}{\textwidth}
  %lresult
  \begin{verbatim}
  \begin{result}
  ... some output ...
  [LR:/tmp/litrepl/python/partial_7b81e1e.txt]
  \end{result}
  \end{verbatim}
  %lnoresult
  \end{minipage}
  \caption{Partial result section with a continuation tag.}
  \label{fig:partial-result}
\end{figure*}

@@

Template grammars similar to the illustrative example in Figure
\ref{fig:document-representation} are encoded for Markdown and \Latex formats.
Before each run, Litrepl calls Lark (\textcite{Lark}) to compile a customized
parser and uses it to access the sections.

@@

The restriction to text-only data types presents a more fundamental limitation.
Litrepl lifts this restriction by supporting text-only document formats. Both
\Latex and Markdown incorporate non-text data without encoding it directly,
instead relying on references and side channels, such as the file system or
network resource identifiers. Consequently, Litrepl shares, for example, the
benefits of human-readable representation in version control systems and the
penalties, such as the need to explicitly organize side-channel data transfer.

@@

A more performance-oriented integrations can make pre-parsing and pipe only
relevant document parts. For these approaches, Litrepl offers the
\verb|print-regexp| command, which outputs the anchor regexp in several common
formats.
% lnoresult
